Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-06-18 paper/ifo-tableTopGWs.tex
adding a few more references

Gravitational-wave detectors are large, complex interferometers.
The LIGO and Virgo detectors have $4\,{\rm km}$ and $3\,{\rm km}$ arms respectively.
They are sensitive to miniscule changes in distance, for example the first detection of a binary black hole merger had a peak gravitational-wave strain of $10^{-21}$ ~\cite{GW150914}.
However, their design is based fundamentally on the Michelson interferometer. 
Detection and analysis concepts can be demonstrated with table-top optical equipment.

@@

>>>>

Gravitational-wave detectors are large, complex interferometers.
The LIGO and Virgo detectors have $4\,{\rm km}$ and $3\,{\rm km}$ arms respectively.
They are sensitive to minuscule changes in distance, for example the first detection of a binary black hole merger had a peak gravitational-wave strain of $10^{-21}$ ~\cite{GW150914}.
However, their design is based fundamentally on the Michelson interferometer. 
Detection and analysis concepts can be demonstrated with table-top optical equipment.

@@

\han{to do: add some text referring to other demo designs and references:~\cite{TTExhibit:2020,TTExhibit:online,ThorLabsIFO,LIGOIFOGlue,LIGOIFOMagnets,FoxEtAl:1999}. }
% Note that we do not include the common compensating plate that equalises the amount of time spent in glass for each beam. We did not find it necessary to include it to be able to demonstrate the results desired.
